Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-05-14 sections/acknowledgements.tex
Making acknowledgements section shorter

\noindent Special thanks to Scott Austin, Ph.D. (Associate Professor of Astronomy and Physics, UCA), Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics), and Shane Ayotte (UCA Mathematics Student).

Our research team practices open-source science. All data and analysis code, along with the source of this paper can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab}

This research would not have been possible without the support of state and federal grants. Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, matched by ASGC state match 20-ARMF-02. Funding to support student research and travel to present our results came from the ASGC Student Intensive Training award. These ASGC awards are subawards of NASA award 80NSSC20M0106.

>>>>

\noindent Special thanks to Scott Austin, Ph.D. (Associate Professor of Astronomy and Physics, UCA), Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics), and Shane Ayotte (UCA Mathematics Student).
All data and analysis code, along with the source of this paper can be accessed at \url{https://github.com/UCA-Open-Astronomy-Lab}.
Funding for this research came from an Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, and an ASGC Student Intensive Training award. These ASGC awards are subawards of NASA award 80NSSC20M0106.
